Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-02-23 bw-prop.tex
tentative draft, needs alex input

While the allocation needs will vary according to the particular simulations, Dr. Huff’s research group will conduct many 2-dimensional and 3-dimensional finite element simulations per year using the MOOSE framework and modules. Such simulations commonly occupy tens of thousands of CPU cores at a time and vary in completion time. The MOOSE framework is shown to scale very well up to 10,000 cores. Transient and multi-scale simulations, which require greater capability per simulation, may occupy up to 100,000 CPU cores at a time. Only a few of those larger simulations are likely to be run per year.

@@

Simulations on the reactor core scale require substantial
computing resources to enable interrogation of
physical phenomena in the complex environments inside a nuclear reactor.

>>>>

Initial simulations of the MSRE have been conducted both locally on the desktop 
computer scale and on Blue Wates. These have been steady state simulations and 
have occupied up to hundreds of nodes simultaneously. Coupling between 
neutronics and thermal hydraulics ahve been established in the Moltres tool, 
though validation and verification efforts are ongoing. In the near term, these 
steady state calculations will provide the initial conditions for full core 
reactor transient simulations. Such simulations commonly occupy tens of 
thousands of CPU cores at a time and vary in completion time. The MOOSE 
framework is shown to scale very well up to 10,000 cores. Transient and 
multi-scale simulations, which require greater capability per simulation, may 
occupy up to 100,000 CPU cores at a time. Only a few of those larger 
simulations are likely to be run this year..

@@
